\newpage
\section{Discussion and Conclusion}

This work described the simulation of an experiment conducted in ref.~\cite{heeg}. Graphene was used as a Raman active material for surface-enhanced Raman spectroscopy with a gold nanodimer as a plasmonic nanostructure. Because the laser spot size is much bigger than the area of the dimer cavity, the calculated local enhancement cannot be directly compared to the experimental enhancement.

It was the scope of this work to draw a comparison between the local simulated enhancement and the total measured enhancement. The shape of the graphene layer, that was suspended on top of the gold nanodimer, was simulated with a 3D modelling software. The local electromagnetic enhancement was calculated with the finite-difference time-domain method, using the commercial software Lumerical FDTD solutions. By averaging the local electromagnetic enhancement at the graphene layer over the size of the laser spot the total enhancement was calculated.

The calculated average enhancement within the simulated area was $60.2$  both for a \SI{2}{nm} corner radius and a \SI{5}{nm} corner radius (both in the plane of graphene) and $59.2$ for the \SI{5}{nm} corner radius for a planar slice at a height of $z=\SI{40}{nm}$. Taking the laser geometry into account the total enhancement was calculated as $38.1$ for the \SI{2}{nm} corner radius, $37.8$ for the \SI{5}{nm} corner radius and $37.2$ for the planar slice. Using the spatial coherence theory of ref.~\cite{coherence} the enhancement of the \SI{5}{nm} planar slice decreased to $23.0$. The corner radius of the gold nanostructure only had a minor influence on the total enhancement, although it led to significant changes in $xz$ contour plots of the near-field.

The simulated local electric field enhancement nicely reproduced the simulation of ref.~\cite{heeg}. Comparing the resulting total enhancement for an accurately modeled geometry of the graphene layer to a slice at the height of \SI{40}{nm} confirmed the approximation used in ref.~\cite{heeg}. Taking spatial coherence effects into account, the resulting total enhancement of $23.0$ reproduced the measured value of $12.8$ in ref.~\cite{heeg} within a factor of two.

Further simulations should include even larger corner radii to find an experimental setup that results in the same near-field at the edges of the nanostructure. Additionally, the presented method can be adapted for other Raman-active materials suspended on nanostructures for
surface-enhanced Raman spectroscopy.
