\subsection{Finite-difference time-domain method}

Plasmonics explores the interaction of metallic surfaces and light waves that causes density waves of electrons on the surface. The electron density wave propagating on the metal is often referred to as a surface plasmon.

While there are other often more efficient methods to numerically simulate and calculate surface plasmons, the finite-difference time-domain method is way more flexible. Because it's basically just a solver for Maxwell's equations without any assumptions on the geometry or effects of the simulation it can calcuate various experiments from Raman scattering to all kinds of light interaction with wavelength-scale 3D metal geometries.

The finite-difference time-domain method (also called Yee's method after the mathematician Kane Yee) describes an algorithm to calculate time dependent electromagnetic fields based on Maxwell's equations. It has first been published in a paper by Kane Yee in 1966\cite{yee}.

To describe a system space and time is broken down into a grid (which can but doesn't have to have equidistant points) which contains information about the electric and magnetic fields and the permittivity at each point. After the grid is initialized, the next electric field values can be calculated from the magnetic field and - in a second step - the future electric field can be calculated from the magnetic field. By taking the permittivity into account this method is capable of describing inhomogenous complex systems that consist of different materials and field sources.
